Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-04 notes.tex
obtained spectral function, plotted it as well
expressed Gkw of general Hubbard in terms of inverse Gs of SIAM

The local Hamiltonians look like
\begin{equation}\begin{aligned}
	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
\begin{equation}\begin{aligned}
	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N. of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
\begin{equation}\begin{aligned}
	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\). Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
\begin{equation}\begin{aligned}
	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
\end{aligned}\end{equation}
For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer. The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
\begin{equation}\begin{aligned}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
In terms of the Green's function, this equation becomes
\begin{equation}\begin{aligned}
	\label{green_eq}
	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\left(\omega - {G_A}^{-1}(\omega)\right)\left(d, z \to i,j\right) + \left(\omega - {G_A}^{-1}(\omega)\right)\left(d,z \to j,i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
where $G_H$ and $G_A$ are the Hubbard and SIAM Green's functions:
\begin{equation}\begin{aligned}
	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
\end{aligned}\end{equation}
Since the two $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor. Each will come with a factor which is just the total number of nearest neighbour pairs, which is $ \frac{Nw}{2}$. This allows them to cancel the $\omega$ on the LHS. The equation then simplifies to
\begin{equation}\begin{aligned}
	\label{green_eq_final}
	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]
\end{aligned}\end{equation}
where $\tilde G_A^{-1}(\omega, i, j) = \omega - \tilde H^A(i, j)$, and $H^A(i, j)$ is defined as
\begin{equation}\begin{aligned}
	\tilde H^A(i, j) = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
$\tilde H^A(i, j)$ is nothing but the Anderson molecule Hamiltonian, but with the impurity replaced by the $i^\text{th}$ site and the zero-mode replaced by the $j^\text{th}$ site. It is important to note that $\tilde G_A^{-1}(\omega, i, j)$ only scatters between the sites $i,j$.

We will now calculate the single-particle site diagonal and site offdiagonal Green's functions. First lets consider the diagonal Green's function at $i^\text{th}$ site. The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices. There will be $w$ such terms, because $i$ has $w$ nearest neighbours. Each such pair will have two terms, one with $i$ as the impurity and another with $i$ as the zero-mode. For the term that has $i$ as the impurity, the Green's function would then represent the impurity-diagonal Green's function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Green's function would represent the bath-diagonal or the zero-mode diagonal Green's function $(G_{zz}^\sigma)$.
\begin{equation}\begin{aligned}
	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]
\end{aligned}\end{equation}
Now we come to the off-diagonal Green's function for the nearest neighbour sites $i$ and $j$. This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$. The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$. The Greens function will thus be the impurity-zero mode and zero mode-impurity Green's functions:
\begin{equation}\begin{aligned}
	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,j\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
\end{aligned}\end{equation}

@@

The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
\begin{equation}\begin{aligned}
	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
\end{aligned}\end{equation}
The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
\begin{equation}\begin{aligned}
	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \mp t
\end{aligned}\end{equation}
for the first inner product, and
\begin{equation}\begin{aligned}
	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \pm t
\end{aligned}\end{equation}
for the second. The Greens function is therefore
\begin{equation}\begin{aligned}
	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
\end{aligned}\end{equation}

>>>>

The local Hamiltonians look like
\begin{equation}\begin{aligned}
	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
\begin{equation}\begin{aligned}
	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N. of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
\begin{equation}\begin{aligned}
	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\). Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
\begin{equation}\begin{aligned}
	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
\end{aligned}\end{equation}
For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer. The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
\begin{equation}\begin{aligned}
	\label{H_tiled}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
\section{Computing Greens functions and related quantities}
In terms of the Green's function, equation \ref{H_tiled} becomes
\begin{equation}\begin{aligned}
	\label{green_eq}
	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\left(\omega - {G_A}^{-1}(\omega)\right)\left(d, z \to i,j\right) + \left(\omega - {G_A}^{-1}(\omega)\right)\left(d,z \to j,i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
where $G_H$ and $G_A$ are the Hubbard and SIAM Green's functions:
\begin{equation}\begin{aligned}
	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
\end{aligned}\end{equation}
Since the two $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor. Each will come with a factor which is just the total number of nearest neighbour pairs, which is $ \frac{Nw}{2}$. This allows them to cancel the $\omega$ on the LHS. The equation then simplifies to
\begin{equation}\begin{aligned}
	\label{green_eq_final}
	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]
\end{aligned}\end{equation}
where $\tilde G_A^{-1}(\omega, i, j) = \omega - \tilde H^A(i, j)$, and $H^A(i, j)$ is defined as
\begin{equation}\begin{aligned}
	\tilde H^A(i, j) = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
$\tilde H^A(i, j)$ is nothing but the Anderson molecule Hamiltonian, but with the impurity replaced by the $i^\text{th}$ site and the zero-mode replaced by the $j^\text{th}$ site. It is important to note that $\tilde G_A^{-1}(\omega, i, j)$ only scatters between the sites $i,j$.

We will now calculate the single-particle site diagonal and site offdiagonal Green's functions. First lets consider the diagonal Green's function at $i^\text{th}$ site. The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices. There will be $w$ such terms, because $i$ has $w$ nearest neighbours. Each such pair will have two terms, one with $i$ as the impurity and another with $i$ as the zero-mode. For the term that has $i$ as the impurity, the Green's function would then represent the impurity-diagonal Green's function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Green's function would represent the bath-diagonal or the zero-mode diagonal Green's function $(G_{zz}^\sigma)$.
\begin{equation}\begin{aligned}
	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]
\end{aligned}\end{equation}
Now we come to the off-diagonal Green's function for the nearest neighbour sites $i$ and $j$. This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$. The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$. The Greens function will thus be the impurity-zero mode and zero mode-impurity Green's functions:
\begin{equation}\begin{aligned}
	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
\end{aligned}\end{equation}
Since the only real-space interaction is that between the nearest neighbours, there are no further real space Green's functions, and the matrix $G^{-1}$ is tridiagonal in real space. Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$. For brevity, we therefore label them $g_0$ and $g_1$ respectively. 
\begin{equation}\begin{aligned}
	g_0 &\equiv \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]\\
	g_1 &\equiv \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
\end{aligned}\end{equation}

\begin{equation}\begin{aligned}
	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
		    &&.&&\\
		    &&.&&\\
		    &&.&&\\
\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
		g_1 & g_0 & g_1 & ... & ...\\
		... & g_1 & g_0 & g_1 & ... \\
		    &&...&&\\
		    &&...&&\\
\end{pmatrix} 
\end{aligned}\end{equation}
It can be written in the operator form as
\begin{equation}\begin{aligned}
	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
\end{aligned}\end{equation}
We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
\begin{equation}\begin{aligned}
	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice. $q_i$ are the projections of $\vec q$ along those vectors. $a_i$ are the lattice spacings along each primitive vector. Adding the Hermitian conjugate simply extracts the real part:
\begin{equation}\begin{aligned}
	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
The inverse Greens function thus becomes diagonal in momentum space
\begin{equation}\begin{aligned}
G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
	& g_0 + g_1\xi_{\vec k_2} && \\
	&& g_0 + g_1\xi_{\vec k_3} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
\begin{equation}\begin{aligned}
	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
\begin{equation}\begin{aligned}
	G_H(\vec k, \omega) &= g_0 + g_1 \xi_{\vec k}\\
			    &= \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}
\end{aligned}\end{equation}

@@

The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
\begin{equation}\begin{aligned}
	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
\end{aligned}\end{equation}
The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
\begin{equation}\begin{aligned}
	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \mp t
\end{aligned}\end{equation}
for the first inner product, and
\begin{equation}\begin{aligned}
	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \pm t
\end{aligned}\end{equation}
for the second. The Greens function is therefore
\begin{equation}\begin{aligned}
	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
\end{aligned}\end{equation}
The site local spectral can now be calculated:
\begin{equation}\begin{aligned}
	A(i\uparrow, \omega) &= - \frac{1}{\pi}\text{Im }G_{i i}^\uparrow(\omega)\\
			     &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right] + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]
\end{aligned}\end{equation}
